SNEAP2021 Figures

### 2021-05-01 doc/SNEAP2021/SNEAP2021_figures.Rmd
rewrite inlet and blank slides. Add inlet diagram. Add current dependent blank figures

combine data from 12-04, 12-11, 12-18,

@@

```{r, message = FALSE}
df <- map_dfr(list.files(here("data_analysed"), full.names = TRUE), read_csv) %>% 
  mutate(fm_normdiff = normFm(mean, fm_consensus),
         fm_sigma = sigma(mean, fm_consensus, merr),
         fmbc_normdiff = normFm(fm_lbc, fm_consensus),
         fmbc_sigma = sigma(fm_lbc, fm_consensus, merr))
```

```{r}
df %>% 
  filter(fm_normdiff < 100) %>% 
ggplot(aes(fm_consensus, fm_normdiff)) +
  geom_hline(yintercept = 0) +
  geom_errorbar(aes(ymin = fm_normdiff - merr, ymax = fm_normdiff + merr)) +
  geom_point() +
  ggtitle("Difference in measured Fm vs. consensus")
```

```{r}
df %>% 
  filter(fm_normdiff < 1) %>% 
ggplot(aes(fm_consensus, fm_normdiff)) +
  geom_hline(yintercept = 0) +
  geom_errorbar(aes(ymin = fm_normdiff - merr, ymax = fm_normdiff + merr)) +
  geom_point() +
  ggtitle("Difference in measured Fm vs. consensus")
```
```{r}
ggplot(df, aes(fm_consensus, diff)) +
  geom_hline(yintercept = 0) +
  geom_errorbar(aes(ymin = diff - merr, ymax = diff + merr)) +
  geom_point() +
  ggtitle("Difference in LBC-corrected vs consensus")
```

@@

>>>>

```{r}
data<- get_hgis_data(here("data/USAMS101320R.txt"), as.Date("2020-11-17")) %>% 
  mutate(Num = ifelse(Pos %in% c(2, 4), "S", ifelse(Num == "S", "U", Num)))
stdrat <- mean(data$cor1412he[data$Num == "S" & !data$outlier])
data1013 <- data %>% mutate(normFm = norm_gas(cor1412he, stdrat))

data <- get_hgis_data(here("data/USAMS120320R.txt"), as.Date("2020-12-04")) %>% 
  mutate(Num = ifelse(Pos %in% c(2, 4), "S", ifelse(Num == "S", "U", Num)))
stdrat <- mean(data$cor1412he[data$Num == "S" & !data$outlier])
data1204 <- data %>% mutate(normFm = norm_gas(cor1412he, stdrat))

data1211 <- get_hgis_data(here("data/USAMS120320R.txt")) %>% 
  filter(Pos %in% 1:4 | as.Date(ts) == "2020-12-11")

data <- get_hgis_data(here("data/USAMS120320R.txt"), as.Date("2020-12-18")) %>% 
  filter(Pos != 0) %>% 
  mutate(Num = ifelse(Pos %in% c(2, 4), "S", ifelse(Num == "S", "U", Num)))
stdrat <- mean(data$cor1412he[data$Num == "S" & !data$outlier])
data1218 <- data %>% mutate(normFm = norm_gas(cor1412he, stdrat))

data0108 <- get_hgis_data(here("data/USAMS120320R.txt"), as.Date("2021-01-08"))

# no solid standards
# df <- get_hgis_data(here("data/USAMS120320R.txt"), as.Date("2021-01-15")) 
# stdrat <- mean(df$cor1412he[df$pos_name == "8 - LiveGasOS" & !df$outlier])
# data0115 <- mutate(df, normFm = norm_gas(cor1412he, stdrat))

data <- get_hgis_data(here("data/USAMS020521R.txt")) %>% 
  mutate(Num = ifelse(Pos %in% c(2, 4), "S", ifelse(Num == "S", "U", Num)))
stdrat <- mean(data$cor1412he[data$Num == "S" & !data$outlier])
data205 <- data %>% mutate(normFm = norm_gas(cor1412he, stdrat))

data <- get_hgis_data(here("data/USAMS030421R.txt"), as.Date("2021-03-05")) %>% 
  mutate(Num = ifelse(Pos %in% c(2, 4), "S", ifelse(Num == "S", "U", Num)))
stdrat <- mean(data$cor1412he[data$Num == "S" & !data$outlier])
data304 <- data %>% mutate(normFm = norm_gas(cor1412he, stdrat))

data <- get_hgis_data(here("data/USAMS040121R.txt"), as.Date("2021-04-09")) %>% 
  mutate(Num = ifelse(Pos %in% c(22, 24), "S", ifelse(Num == "S", "U", Num)))
stdrat <- mean(data$cor1412he[data$Num == "S" & !data$outlier])
data409 <- data %>% mutate(normFm = norm_gas(cor1412he, stdrat))

data <- get_hgis_data(here("data/USAMS041521R.txt"), as.Date("2021-04-16"))  %>% 
  mutate(Num = ifelse(Pos %in% c(22, 24), "S", ifelse(Num == "S", "U", Num)))
stdrat <- mean(data$cor1412he[data$Num == "S" & !data$outlier])
data415 <- data %>% mutate(normFm = norm_gas(cor1412he, stdrat))

std <- getStdTable()

data <- rbind(data1013, data1204, data1211, data1218, data205, data304, data409, data415) %>% 
  mutate(rec_num = case_when(str_detect(Sample.Name, "LiveGas") ~ 101730,
                             str_starts(Sample.Name, "C-1") ~ 83028,
                             str_starts(Sample.Name, "C1") ~ 83028,
                             str_starts(Sample.Name, "TIRI-F") ~ 2138,
                             str_starts(Sample.Name, "TIRI-I") ~ 17185,
                             str_starts(Sample.Name, "C-2") ~ 1082,
                             str_starts(Sample.Name, "C2") ~ 1082,
                             str_starts(Sample.Name, "NOSAMS") ~ 38809,
                             str_detect(Sample.Name, "DeadGas") ~ 72446)) %>% 
 left_join(select(std, rec_num, fm_consensus), by = "rec_num") %>% 
 mutate(fm_consensus = case_when(rec_num == 101730 ~ 1.0398,
                                 rec_num == 72446 ~ 0.0013,
                                 TRUE ~ fm_consensus))

xl <- 8

livefm_cur <- data %>% 
  filter(!(he12C < 2.5 & normFm > 1.05) & fm_consensus > 0.9) %>% 
  ggplot(aes(he12C, normFm)) + 
  geom_point() +
  xlim(0, xl) +
  ylim(.8, 1.2) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank())

deadfm_cur <- data %>% 
  filter(fm_consensus < 0.1 & normFm < 0.3 & Sample.Name != "DilDeadGas6") %>% 
  ggplot(aes(he12C, normFm)) + 
  geom_point() +
  xlim(0, xl) +
  ylim(0, .4)

livefm_cur / deadfm_cur
```

### Current dependent model

```{r}
ds <- sum_hgis(data) %>% 
  filter((str_detect(Sample.Name, "LiveGas") & Cur > 1) |
         (str_detect(Sample.Name, "DeadGas") & Cur > 1) |
          str_detect(Sample.Name, "Blank")) %>% 
  mutate(Gas = case_when(str_detect(Sample.Name, "LiveGas") ~ "LiveGas",
                         str_detect(Sample.Name, "DeadGas") ~ "DeadGas",
                         TRUE ~ "Blank"),
         Cur_inv = 1/Cur)

# Fit linear model
fits <- ds %>% 
  ungroup() %>% 
  nest(data = -Gas) %>% 
  mutate(fit = map(data, ~lm(mean ~ Cur_inv, data = .x)),
         tidied = map(fit, tidy)) %>% 
  unnest(tidied)

blankfit <- fits %>% 
  select(Gas, term, estimate) %>% 
  pivot_wider(names_from = c(Gas, term), values_from = estimate) %>% 
  mutate(inv_m_blank = -(`DeadGas_(Intercept)` - `LiveGas_(Intercept)`)/(DeadGas_Cur_inv - LiveGas_Cur_inv),
         Fm_blank = `DeadGas_(Intercept)` + DeadGas_Cur_inv * inv_m_blank,
         m_blank = 1/inv_m_blank)

# Modeled Fm and mass of blank
blankfit %>% 
  select(Fm_blank, m_blank)

# Plot of data and model with measured blanks
ggplot(ds, aes(Cur_inv, mean, color = Gas)) +
  geom_abline(slope = blankfit$LiveGas_Cur_inv, 
              intercept = blankfit$`LiveGas_(Intercept)`) +
  geom_abline(slope = blankfit$DeadGas_Cur_inv, 
              intercept = blankfit$`DeadGas_(Intercept)`) +
  geom_pointrange(aes(ymin = mean - merr, ymax = mean + merr), size = .3) + 
  xlim(0, 10) +
  #ylim(0, 1.2)
  ggtitle("Fm of live and dead CO2 vs. inverse 12C current",
          subtitle = "Fit lines should cross at Fm and current of blank")
```

@@

```{r, message = FALSE}
df <- map_dfr(list.files(here("data_analysed"), full.names = TRUE), read_csv) %>% 
  filter(!is.na(rec_num)) %>% 
  mutate(fm_diff = mean - fm_consensus,
         fm_sigma = sigma(mean, fm_consensus, merr),
         fmbc_diff = fm_lbc - fm_consensus,
         fmbc_sigma = sigma(fm_lbc, fm_consensus, merr))
```

### difference from consensus

```{r, fig.height=5, dev='svg'}

dfc <- df %>% 
  filter(Cur > 2)

ps <- 0.3
dw <- 0.03
yl <- .1

secs <- ggplot(dfc, aes(fm_consensus, fm_diff, color = Cur)) +
  geom_hline(yintercept = 0) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_pointrange(aes(ymin = fm_diff - merr, ymax = fm_diff + merr), 
                  position = position_dodge2(width = dw),
                  size = ps,) +
  #geom_point() +
  lims(x = c(-0.05, 1.1),
       y = c(-yl, yl)) +
  labs(title = "Difference from consensus",
       subtitle = "Uncorrected",
       y = "Fm difference") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        legend.direction = "horizontal",
        legend.position = c(.88, 1),
        legend.justification = "bottom")

secs_lbc <- ggplot(dfc, aes(fm_consensus, fmbc_diff, color = Cur)) +
  geom_hline(yintercept = 0) +
  geom_smooth(method = "lm", se = FALSE) +
  #geom_hline(yintercept = mean_diff) +
  geom_pointrange(aes(ymin = fmbc_diff - merr, ymax = fmbc_diff + merr), 
                  position = position_dodge2(width = dw),
                  size = ps) +
  #geom_point() +
  lims(x = c(-0.05, 1.1),
       y = c(-yl, yl)) +
  labs(subtitle = "LBC-corrected",
       x = "Fm consensus",
       y = "Fm difference") +
  theme(legend.position = "None")

secs / secs_lbc
```
### same for sigma

@@

### Blanks - current independent

```{r}
dfc
```
